In this section, we will implement a finite volume method to solve the problem given.

\subsection{Finite Volume method}
First, we need to define the method used. Let us start with the PDE and take the average over cell $(i,j)$.

$$\frac{1}{\Delta x \Delta y}\iint_{(i,j)} q_t dxdy = \frac{1}{\Delta x \Delta y} (\iint_{(i,j)} \nabla \cdot (\nabla q)dxdy + \iint_{(i,j)} S\: dxdy) $$

Using the definition of $Q_{ij}$, divergence theorem and defining $S_{ij}(t) =\frac{1}{\Delta x \Delta y}\iint_{(i,j)} S\: dxdy$ , we get :
$$\frac{dQ_{ij}}{dt} = \frac{1}{\Delta x \Delta y}\oint_{(i,j)} \nabla q \cdot \textbf{n}\: ds + S_{ij}(t)$$

Because each cell is a rectangle, the first term in the right-hand side can be expressed as the sum of the integral evaluated at each side (East, North, West and South) : 
$$\oint_{(i,j)} \nabla q \cdot \textbf{n}\: ds = \int_E q_x dy+\int_N q_ydx-\int_Wq_xdy-\int_Sq_ydx$$

The next step is to discretize those integral. We will use finite differences. Let us assume that we are not on the boundary.

\begin{align*}
\int_E q_xdy &\approx \Delta y \frac{Q_{i+1,j}-Q_{i,j}}{\Delta x}\\
\int_W q_xdy &\approx -\Delta y \frac{Q_{i-1,j}-Q_{i,j}}{\Delta x}\\
\int_N q_ydx &\approx \Delta x \frac{Q_{i,j+1}-Q_{i,j}}{\Delta y}\\
\int_S q_ydx &\approx -\Delta x \frac{Q_{i,j-1}-Q_{i,j}}{\Delta y}
\end{align*}

If we are on the boundary, we use the boundary condition to have : 
\begin{align*}
i=1 &\implies \int_W q_ydx = 0\\
i=m &\implies \int_E q_ydx = 0\\
j=1 &\implies \int_S q_xdy = 0\\
j=n &\implies \int_N q_xdy = 0
\end{align*}

Using the finite differences above, in general, we have the following discrete equation : 
$$\frac{dQ_{ij}}{dt} = \frac{aQ_{i+1,j}+bQ_{i,j}+cQ_{i-1,j}}{\Delta x^2}+\frac{dQ_{i,j+1}+eQ_{i,j}+fQ_{i,j-1}}{\Delta y^2}+S_{ij}(t)$$

Where $a,b,c,d,e,f$ are given in the two tables below : 
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline 
 & a & b & c \\ 
\hline 
i = 1 & 1 & -1 & 0 \\ 
\hline 
i = 2:m-1 & 1 & -2 & 1 \\ 
\hline 
i = m & 0 & -1 & 1 \\ 
\hline 
\end{tabular} 
\begin{tabular}{|c|c|c|c|}
\hline 
 & d & e & f \\ 
\hline 
j = 1 & 1 & -1 & 0 \\ 
\hline 
j = 2:n-1 & 1 & -2 & 1 \\ 
\hline 
j = n & 0 & -1 & 1 \\ 
\hline 
\end{tabular} 
\end{center}

In order to solve this numerically, we also need to rewrite the unknown matrix $Q$ as a vector. We do this by defining $Qvect$ as :
$$Qvect_k = Q_{i,j}   \iff k = (j-1)m + i$$

So we now get a system of linear ODE's to solve (where $M$ is a $mn \times mn$ matrix) : 
$$\frac{dQvect}{dt} = MQvect + S$$

The only remaining thing to do is to build $M$. In order to do this let us define $I(c)$ the $c\times c $ identity matrix and $A(c)$ the following $c\times c $ : 
$$A = \left(\begin{array}{ccccc}
-1 & 1 & 0 & \cdots & 0 \\ 
1 & -2 & 1 & \cdots & 0 \\ 
0& \ddots & \ddots & \ddots & 0 \\ 
0 & \cdots & 1 & -2 & 1 \\
0 & \cdots & 0 & 1 & -1
\end{array}\right) $$

We can now build $B$, representing the $x$-derivative : 
$$B = \frac{1}{\Delta x^2}I(n)\otimes A(m)$$

Where $\otimes$ is the kronecker product. We can check that the size of $B$ is indeed $mn \times mn$ because $A(m)$ is of size $m \times m$.

We can also build $C$, representing the $y$-derivative : 
$$C = \frac{1}{\Delta y^2}\left(\begin{array}{ccccc}
-I(m) & I(m) & 0 & \cdots & 0 \\ 
I(m) & -2I(m) & I(m) & \cdots & 0 \\ 
0& \ddots & \ddots & \ddots & 0 \\ 
0 & \cdots & I(m) & -2I(m) & I(m) \\
0 & \cdots & 0 & I(m) & -I(m)
\end{array}\right) =\frac{1}{\Delta y^2} A(n)\otimes I(m)$$

Finally : 
$$M = B + C$$

\subsection{Implicit Euler}

Now that the problem is spatially discretized, we can start solving the system of ODE's. Let us first introduce the time step $\Delta t$ and some notation :
$$Qvect^{(T)} \approx Qvect(T\Delta t)$$
$$S_k^{(T)} \approx \frac{1}{\Delta x \Delta y}\iint_{(i,j)} S(x,y,T\Delta t)dxdy$$

Because, for the second heat source, $S$ depends on $t$. We also have to numerically compute the mean of the heat source on each cell. We will use the classic central point approximation. 
$$S_k^{(T)} = S(x_i,y_j,T\Delta t)$$

We can now use implicit euler for the time derivative. We also have to remember that $M$ does not depends on $t$ and thus :

$$\frac{Qvect^{(T+1)}-Qvect^{(T)}}{\Delta t} = MQvect^{(T+1)} + S^{(T+1)}$$

If $Id$ is the $mn\times mn$ identity matrix, we have :
$$(Id-\Delta t M)Qvect^{(T+1)} = Qvect^{(T)} + S^{(T+1)}$$

$Qvect^{(0)}$ is filled with zeroes because of the initial condition and the equation above gives the recursion to compute every $Qvect$. We can then reshape $Qvect$ to obtain the matrix $Q$. \\


Here, implicit euler is used because the problem is stiff ($M$ has eigenvalues of very different magnitudes). Thus, an explicit method would require us to take a very little time step in order to have a stable solution. The use of an implicit method allows us to take a much bigger time step and thus to be more efficient.

\subsection{Problem in matrix form}
It is convenient to use the matrix form because we do not have to think about changing lines to take the boundary conditions into account and we thus avoid kronecker products.

If we use this to state the problem, we have : 
$$\frac{dQ}{dt}=QT_x+T_yQ+S$$

Using implicit euler and the same notation as before, we get :
$$\frac{Q^{(T+1)}-Q^{(T)}}{\Delta t} = Q^{(T+1)}T_x+T_yQ^{(T+1)}+S$$
$$Q^{(T+1)} - \Delta t Q^{(T+1)}T_x - \Delta t T_yQ^{(T+1)} = Q^{(T)}+\Delta t S$$

This recursion equation is unfortunately not solvable because $Q^{(T+1)}$ is multiplied on the left once and on the right another time. This is why we have to write $Q$ as a vector to solve the problem with implicit euler.

However, the matrix form allows us to prove that the finite volume method is exactly conservative. Indeed, since the walls are insulated, if the source term is 0, we should keep the same amount of heat in the domain.
$$\frac{d}{dt}\int_0^1\int_0^1 Qdxdy = 0$$

Let us see if that is indeed the case for our method. Because $Q_{ij}$ is defined as the average on cell $(i,j)$, we have that :
$$\int_0^1\int_0^1 Qdxdy = \Delta x \Delta y \sum_i\sum_j Q_{ij}$$

So we only have to prove that, in the absence of a source term, the sum of all entries does not vary in time. Since summing a matrix is multiply it by vectors filled with zeroes :
$$\frac{d}{dt}(\left(\begin{array}{ccc}
1 & \cdots & 1
\end{array}\right) Q \left(\begin{array}{c}
1 \\ 
\vdots \\ 
1
\end{array}\right) ) = \left(\begin{array}{ccc}
1 & \cdots & 1
\end{array}\right) \frac{dQ}{dt} \left(\begin{array}{c}
1 \\ 
\vdots \\ 
1
\end{array}\right)$$

Using our scheme (and remembering that the source term is 0...), we get : 
$$ \left(\begin{array}{ccc}
1 & \cdots & 1
\end{array}\right) \frac{dQ}{dt} \left(\begin{array}{c}
1 \\ 
\vdots \\ 
1
\end{array}\right)=\left(\begin{array}{ccc}
1 & \cdots & 1
\end{array}\right)QT_x \left(\begin{array}{c}
1 \\ 
\vdots \\ 
1
\end{array}\right) +\left(\begin{array}{ccc}
1 & \cdots & 1
\end{array}\right)T_yQ\left(\begin{array}{c}
1 \\ 
\vdots \\ 
1
\end{array}\right)$$

Because of the structure of $T_x$ and $T_y$, we also have :
$$T_x \left(\begin{array}{c}
1 \\ 
\vdots \\ 
1
\end{array}\right)=\left(\begin{array}{c}
0 \\ 
\vdots \\ 
0
\end{array}\right)$$
$$\left(\begin{array}{ccc}
1 & \cdots & 1
\end{array}\right)T_y=\left(\begin{array}{ccc}
0 & \cdots & 0
\end{array}\right)$$

So the right hand side is equal to zero.

We can then conclude that the finite volume method is exactly conservative.


\subsection{Approximation of the dirac}
Remember that the discretized problem says : 
$$S_k^{(T)} = S(x_i,y_j,T\Delta t)$$

But, when $S$ is the dirac function, we cannot do that because it is impossible to evaluate the dirac function. So, we will approximate it by the given function.

\subsection{Implementation}
The Matlab code for the implementation of the finite volume method for this problem can be found at the end of the report.

